Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-05-29 snapshot_system/arch.tex
w

\section{Design Overview}
%[describe what is going to be presented in this section]
We start by analyzing the main features in the design of our system.
We first present its architecture,
then introduce the two major contributions: the colocated deduplication 
scheme and the snapshot deletion strategy.
\subsection{Architecture}
%[describe the cloud environment]
Our architecture, as shown in figure.\ref{fig:arch}, is built on top of 
Alibaba's platform which is the largest cloud service provider in China. 
A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of xen-based\cite{Barham2003} VMs.
Alibaba's cloud platform provides a hadoop-like infrastructure, 
which includes several highly scalable distributed service:
\begin{description}
\item[Distributed file system] This is a scalable distributed file system (DFS) being optimized for many large and sequential reads or appends. DFS holds the responsibility of managing physical disk storage
in the cloud. All data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
%\item[KV]: a distributed key-value store for managing structured data.
%\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
\item[Distributed memory cache]: A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inqueries. 
\end{description}
In addition, our implementation also uses MapReduce to facilitate the offline
data processing, and stores a small amount of snapshot metadata in a 
BigTable-like persistent key-value store.

%[describe the benefits of using mature cloud technologies]
In general, our snapshot system and the virtual machine management service 
rely on these fundamental cloud services
to be functional. Such a colocated deduplication architecture allow us 
to enjoy the benefits from these mature technologies 
such as load balancing, scalability, and fault tolerancy.
Moreover, all the above cloud services can easily find their open-source counterparts,
which improves the generality of our architecture and deduplication scheme.

{\bf Snapshot Representation}
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit 
in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break 
segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/snapshot_representation.pdf, width=3.7in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot_rep}
\end{figure}
As a result, the representation of each snapshot is designed as a two-level index data structure 
in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot_rep}.
A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
that holds the meatdata of its chunks. We choose this two-level structure because in practice we
observe that during each backup period only a small amount of VM data are added or modified. 
As the result, even the metadata of two snapshots can be highly similar, 
thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
segments which greatly ease the segment-level deduplication.

In both two kind of recipes, 
they do not include the actual data but only have
 references point to the data which are either stored in append store or CDS.
In our implementation the data reference is a 8 bytes field which is either an 
ASID (discuss in \ref{sect:append}) or an offset of an additional flag indicates
the location of CDS data.

\begin{figure}
    \centering
    \subfigure[Node architecture from VM point of view]
    {
        \includegraphics[width=3in]{images/socc_arch_vm.pdf}
        \label{fig:arch_vm}
    }
    \\
    \subfigure[Cluster architecture]
    {
        \includegraphics[width=3in]{images/socc_arch_cluster.pdf}
        \label{fig:arch_cluster}
    }
    \caption{System architecture}
    \label{fig:arch}
\end{figure}

%[describe the architecture frm node side]
{\bf Node Architecuture} 
Our node-side architecture, depicted in figure.\ref{fig:arch_vm}, consists of
two main entities: a virtual block device driver, and a snapshot deduplication component.

%[brief the virtual device driver]
One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
This driver maintains a map of dirty-bits to record
the change status of every fix-size segment of the virtual disk. 
When the VM issue a disk write, the bits coresponding to the segments that covers 
the modified disk region are set, thus letting snapshot deduplication component knows these
segments must be checked during snapshot backup. After the snapshot backup is finished, 
snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
a clean state.

%[brief the snapshot deduplication]
The snapshot deduplication component consists of the chunking and deduplication 
logic of our snapshot storage system. We choose

It contains an append store client which provides facilities to manage stored snapshot data, and a CDS client to support CDS index access. We will further discuss our deduplication scheme in section\ref{sec:dedup}.

%[describe the arch from cluster side]
{\bf Cluster Architecture}

%[describe the data structure in underlying storage]
{\bf Append Store}
Append Store (AS) is our underlining storage engine for storing snapshot data after deduplication. 
AS is built on top of our highly scalable distributed file system (DFS), 
which is very similar to Google's file system
in a sense that it is optimized for large files and sequential read/append operations.

@@

Append Store supplies three interfaces: {\em get(ref)} accepts a data reference and retrives data, 
{\em put(data)} accepts data and returns a reference to be stored in metadata recipes, 
{\em delete(ref)} 
deletes the data pointed by the reference.
Under the hood, small var-sized data are grouped and stored into larger data containers. Each VM has
its snapshot data stored in its own Append Store, specified by the VM ID. 
We split every Append Store into multiple data containers so that reclaiming the disk space would not 
result in rewriting all the data at the same time.

@@

Write requests to append store are accumlated. When the number reaches $m$, the AS client forms a CBlock by assigning 
every chunk a CID, compress the CBlock data, and append it to the CBlock data file. Then a new CBlock index entry is appended
to CBlock index.

@@

\subsection{Snapshot Deduplication and Fault Isolation}
\label{sect:dedupe}
%snapshot representation
%\subsection{Inner and corss VM deduplication}
Our  deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
Such localization increases data independency between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize 
the cost of deduplication while maximize the its efficiency at each level,
and it is parallel since each segment is processed independently.

\begin{itemize}
\item \textbf{Dirty-based corase-grain inner-VM deduplication.}
The first-level deduplication is to follow the standand dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports dirty bits for thestorage device
and the dirty bit setting is maintained in a corase grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
and cannot affort a small segment  size.

@@

The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}.
Thus the second-level inner-VM deduplication is to assess in this
level, but only for those dirty  segments. 
We load the fingerprints of block chunks of the corresponding segment from the
parent for a comparisons and compare near-by fingerprint matching within this segement.
The amount of memory for maintaining those fingerprints  is small.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

\item \textbf{Cross-VM deduplication.}
This step accomplishes the standand global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of duplicates.
There are not lot of deduplication opportunities cross VMs while the memory
consumption for global comparison is expensive.
Thus our approximation is that duplicate sharing patterns among  VM follows
a zip-like distribution, and the global fingerprint  comparison  only searches
for the most popular items. 
\end{itemize}

{\bf Popular Chunk Management and VM-oriented Fault Isolation}
Our objective for fault isolation is to minimize the number of VMs affected when there are failures
in the cluster.  The inner-VM deduplication does not depend on any global service and the comparison
for each VM is localized within the parent and the current snapshot.
Thus there is no data dependence between VMs.
For cross-VM deduplication, there is a data dependence among VMs and we would minimize the faiulre impact
of shared blocks by adding extra replcas of those shared blocks.

This section analyzes the choice of popular blocks and its impact on the deduplication efficiency.
It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
global deduplication.

@@

\subsection{Snapshot Summaries for Deletion}

>>>>

\section{Architecture and Implementation Details}
%[describe what is going to be presented in this section]
%We start by analyzing the main features in the design of our system.
%We first present its architecture,
%then introduce the two major contributions: the colocated deduplication 
%scheme and the snapshot deletion strategy.
%\subsection{Architecture}
%[describe the cloud environment]

%Our architecture, as shown in figure.\ref{fig:arch}, is built on top of 
%Alibaba's platform which is the largest cloud service provider in China. 
%A typical VM cluster in our cloud environment
%consists of from hundreds to thousands of physical machines, each of which can
%host tens of xen-based\cite{Barham2003} VMs.
%Alibaba's cloud platform provides a hadoop-like infrastructure, 
%which includes several highly scalable distributed service:

Our system runs on a cluster of Linux machines with Xen-based VMs.
A distributed file system (DFS) manages  the physical disk storage and we use 
QFS~\cite{QFS}. 
All data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).

\comments{
\begin{description}
\item[Distributed file system] This is a scalable distributed file system (DFS) being optimized for many large and sequential reads or appends. DFS holds the responsibility of managing physical disk storage
in the cloud. 
All data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
%\item[KV]: a distributed key-value store for managing structured data.
%\item[MapReduce]: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
\item[Distributed memory cache]: A distributed memory object caching system helps us to hold the fingerprints of those popular data blocks for deduplication inquiries. 
\end{description}
In addition, our implementation also uses MapReduce to facilitate the offline
data processing, and stores a small amount of snapshot metadata in a 
BigTable-like persistent key-value store.

%[describe the benefits of using mature cloud technologies]
In general, our snapshot system and the virtual machine management service 
rely on these fundamental cloud services
to be functional. Such a co-located deduplication architecture allow us 
to enjoy the benefits from these mature technologies 
such as load balancing, scalability, and fault tolerance.
Moreover, all the above cloud services can easily find their open-source counterparts,
which improves the generality of our architecture and deduplication scheme.

{\bf Snapshot Representation}
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit 
in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.
}

\subsection{ Components of a cluster node }

As  depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication component,
3) an append store client which provides facilities to store  and access snapshot data,
and 4)  a CDS client to support CDS index access. We will further discuss our deduplication scheme 
in Section~\ref{sec:dedup}.

We use the virtual device driver in Xen that employs a bitmap to track the changes 
that have been made to virtual disk.
%This driver maintains a map of dirty bits to record the change status of every fix-size segment of the virtual disk. 
When the VM issue a disk write, the bits corresponding to the segments that covers 
the modified disk region are set, thus letting snapshot deduplication component knows these
segments must be checked during snapshot backup. After the snapshot backup is finished, 
snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
a clean state.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit 
in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
As a standard practice, segments are further divided into variable-sized chunks (average 4KB) 
using content-based chunking algorithm, which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

The representation of each snapshot has  a two-level index data structure.
%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
The snapshot meta data (called snapshot recipe) contains a list of segments, each of which contains segment
metadata of its chunks (called segment recipe).
%\begin{figure}[htbp]
%  \centering
%  \epsfig{file=images/snapshot_representation.pdf, width=3in}
%  \caption{An example of snapshot representation.}
%  \label{fig:snapshot_rep}
%\end{figure}
%As a result, the representation of each snapshot is designed as a two-level index data structure 
%in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot_rep}.
%A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
%that holds the meatdata of its chunks. We choose this two-level structure because in practice we
%observe that during each backup period only a small amount of VM data are added or modified. 
%As the result, even the metadata of two snapshots can be highly similar, 
%thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
%Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
%segments which greatly ease the segment-level deduplication.
In a snapshot recipes or a segment recipe, 
the data structures  includes reference pointers to the actual data location.
%In our implementation the data reference is a 8 bytes field which is either an 
%ASID (discuss in Section \ref{sect:append}) or an offset of an additional flag indicates
%the location of CDS data.

%\subsection{ Snapshot management}

\begin{figure}
    \centering
    \subfigure[Node architecture from VM point of view]
    {
        \includegraphics[width=3in]{images/socc_arch_vm.pdf}
        \label{fig:arch_vm}
    }
    \\
    \subfigure[Cluster architecture]
    {
        \includegraphics[width=3in]{images/socc_arch_cluster.pdf}
        \label{fig:arch_cluster}
    }
    \caption{System architecture.}
    \label{fig:arch}
\end{figure}

%[describe the architecture frm node side]
%[brief the virtual device driver]
%One physical node hosts tens of VMs, each of which access its virtual machine disk image through the
%virtual block device driver (called TapDisk\cite{Warfield2005} in Xen).
%This driver maintains a map of dirty-bits to record
%the change status of every fix-size segment of the virtual disk. 
%When the VM issue a disk write, the bits coresponding to the segments that covers 
%the modified disk region are set, thus letting snapshot deduplication component knows these
%segments must be checked during snapshot backup. After the snapshot backup is finished, 
%snapshot deduplication component acknowledges the driver to resume the dirty-bits map to
%a clean state.

%[brief the snapshot deduplication]
%The snapshot deduplication component consists of the chunking and deduplication 
%logic of our snapshot storage system. We choose

%[describe the arch from cluster side]

%[describe the data structure in underlying storage]
\subsection{Append store for backup data}
The Append Store (AS) is our underlining storage engine for storing snapshot data in the distributed file system
after deduplication.
%AS is built on top of our highly scalable distributed file system (DFS), 
%which is very similar to Google's file system
%in a sense that it is optimized for large files and sequential read/append operations.

@@

AS supplies three interfaces: {\em get(ref)} accepts a data reference and retrieves data, 
{\em put(data)} accepts data and returns a reference to be stored in metadata recipes, 
{\em delete(ref)} 
deletes the data pointed by the reference.
Under the hood, small var-sized data are grouped and stored into larger data containers. Each VM has
its snapshot data stored in its own Append Store, specified by the VM ID. 
We split every Append Store into multiple data containers so that reclaiming the disk space would not 
result in rewriting all the data at the same time.

@@

Write requests to append store are accumulated. When the number reaches $m$, the AS client forms a CBlock by assigning 
every chunk a CID, compress the CBlock data, and append it to the CBlock data file. Then a new CBlock index entry is appended
to CBlock index.

@@

\comments{
\subsection{Snapshot Deduplication and Fault Isolation}
\label{sect:dedupe}
%snapshot representation
%\subsection{Inner and corss VM deduplication}
Our  deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
This process performs   the duplication in two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
Such localization increases data independence between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize 
the cost of deduplication while maximize the its efficiency at each level,
and it is parallel since each segment is processed independently.

\begin{itemize}
\item \textbf{Dirty-based coarse-grain inner-VM deduplication.}
The first-level deduplication is to follow the standard dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports dirty bits for the storage device
and the dirty bit setting is maintained in a coarse grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a block will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment  size.

@@

The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}.
Thus the second-level inner-VM deduplication is to assess in this
level, but only for those dirty  segments. 
We load the fingerprints of block chunks of the corresponding segment from the
parent for a comparisons and compare near-by fingerprint matching within this segment.
The amount of memory for maintaining those fingerprints  is small.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

\item \textbf{Cross-VM deduplication.}
This step accomplishes the standard global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of duplicates.
There are not lot of deduplication opportunities cross VMs while the memory
consumption for global comparison is expensive.
Thus our approximation is that duplicate sharing patterns among  VM follows
a zip-like distribution, and the global fingerprint  comparison  only searches
for the most popular items. 
\end{itemize}

{\bf Popular Chunk Management and VM-oriented Fault Isolation}
Our objective for fault isolation is to minimize the number of VMs affected when there are failures
in the cluster.  The inner-VM deduplication does not depend on any global service and the comparison
for each VM is localized within the parent and the current snapshot.
Thus there is no data dependence between VMs.
For cross-VM deduplication, there is a data dependence among VMs and we would minimize the failure impact
of shared blocks by adding extra replicas of those shared blocks.

This section analyzes the choice of popular blocks and its impact on the deduplication efficiency.
It also  compares the  fault resilience of our VM-centric deduplication approach with a standard approach using 
global deduplication.

@@

\subsection{Snapshot Summaries for Deletion}
}

### 2013-05-29 snapshot_system/intro.tex
w

\section{Introduction}
In a cluster-based cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} 
and Alibaba Aliyun\cite{Aliyun},
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
%Backup  of virtual disks is relatively straightforward since
%these image files are stored as regular files from the external point of view,
%backing up VM's data is mainly done by taking snapshots of virtual disk images.

%A snapshot preserves the data of a VM's file system at a specific point in time. 
%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
For example, the Aliyun cloud , which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.
The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand and  
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
can effectively identify content duplicates among snapshots and  remove 
redundant storage content,  but the solution can be expensive and there is a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

This paper seeks for a low-cost architecture option and considers that
a backup service collocates  on  the cloud cluster with a minimum resource usage. 
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
On the other hand, comparing fingerprints  adds significant  memory cost. 
Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
Cloud providers often wish that the backup service only consumes  small or modest resources
with a minimal impact to the existing cloud services.  A 
recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
Another issue is that after deduplication, the most of data blocks are shared by many virtual machines.
Failure of such blocks would  have a catastrophic effect and many snapshots of virtual machines would be affected.
Furthermore, 
%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
deletion of old snapshots compete for computing resource as well and that  needs
to be considered. That is  because data dependence created
by duplicate relationship among snapshots  adds processing complexity.
% especially when  VMs can migrate around in the cloud.

>>>>

\section{Introduction}
In a cluster-based cloud environment,
% such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
%Backup  of virtual disks is relatively straightforward since
%these image files are stored as regular files from the external point of view,
%backing up VM's data is mainly done by taking snapshots of virtual disk images.
%A snapshot preserves the data of a VM's file system at a specific point in time. 
%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.
The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand and  
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
can effectively identify content duplicates among snapshots and  remove 
redundant storage content,  but the solution can be expensive and there is a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

This paper seeks for a low-cost architecture option and considers that
a backup service collocates  on  the cloud cluster with a minimum resource usage. 
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
%On the other hand, comparing fingerprints  adds significant  memory cost. 
%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
Cloud providers often wish that the backup service only consumes  small or modest resources
with a minimal impact to the existing cloud services.  
We study and evaluate the integration of several deduplication strategies to meet
the low-cost collocation requirement. In parallel, we identify deduplication options that yield
better fault isolation.
%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
This is because  after deduplication, the most of data blocks are shared by many virtual machines.
Failure of such blocks would  have a catastrophic effect and many snapshots of virtual machines would be affected.
The previous work in deduplication focuses on the efficiency and approximation of
finger print comparison, and has not addressed the  fault tolerance along with a low-cost solution.
Another issue considered is that
%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
deletion of old snapshots compete for computing resource as well and that  needs
to be considered. That is  because data dependence created
by duplicate relationship among snapshots  adds processing complexity.
% especially when  VMs can migrate around in the cloud.
